Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-28 paper/ms.tex
update manuscript

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
The relative importance of cooling and photoevaporation is set by the
planetary surface gravity, as well as the radiation environment.  The
timescale for core-powered mass loss may in some cases exceed the
$\sim$100 Myr during which photoevaporation is expected to be
effective \citep{ginzburg_superearth_2016,owen_evaporation_2017}.
Both processes could be directly observed through observations of
planetary winds in the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26, and
CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
Follow-up by Damasso et al{.} (2020, submitted) did not detect
the planetary signal in V830~Tau.

>>>>

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
Reported timescales for photoevaporation and core-powered mass loss
range from 10$\,$Myr to over 1$\,$Gyr for typical transiting
sub-Neptunes
\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
The relative importance of each process is set by the planetary surface
gravity and the radiation environment.  Both processes can be
directly observed through observations of planetary winds in the
metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26, and
CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
%Follow-up by Damasso et al{.} (2020, submitted) did not detect
%the planetary signal in V830~Tau.
